The Country-level Impact of Educational Features on the Rate of Entrepreneurship - Data Gathering and Analysis

### 2014-11-13 GEMDataSource.Rmd
Update GEMDataSource.Rmd

#### Data

@@

Besides these nine conditions and the GEM "perceived opportunities" measure, we also intend to control for the economic outlook at the time of data collection which is why we chose to include growth rate for each country from 2001 until 2013. This is our only data that does not originates from the GEM collection.

### Conclusion

>>>>

#### Data Collection

@@

Besides these nine conditions and the GEM "perceived opportunities" measure, we also intend to control for the economic outlook at the time of data collection which is why we chose to include GDP annual growth rate for each country from 2001 until 2013. This is our only data that does not originates from the GEM collection.

#### Data Scraping and Cleaning

In order to scrape our data, we used repmis, tidyr, reshape2, plyr, WDI, stargazer and Zelig packages. We then imported one dataset per variable mentioned above:
GEM Established Entrepreneurship Rate
GEM Nascent Entrepreneurship Rate
GEM Entrepreneurial Intention
GEM Perceived Capabilities
GEM Fear of Failure
GEM Perceived Opportunities
GDP Annual Growth Rate

.

### Summary
